Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-07-16 ltx/data_paper/DataPaper.tex
edits to discussion

While EKS has been  applied in the context of EM algorithm for learning a nonlinear model from data \cite{Ghahramani1999} this is the first work (to the best authors' knowlege) where the URTSS has been used to perform state inference in the E-step of the EM algorithm. However, as in the case of EKS since an approximate lower bound is maximised at each time step there is no guarantee that URTSS increases the lower bound on the true likelihood function and therefore the stability of the algorithm cannot be ensured. Nevertheless, the proposed framework is more stable due to better performance of the URTSS.
\begin{itemize}
	\item itterative EM and correlation analysis (maybe)
	\item{comment on EM might convrge to suboptimal solution,simulated
annealing can be used to tackle such situations but difficult to implement (Mc Lachlan)}
	\item{since the non-linearity is a sigmoid function first-order Taylor provide a good approximation however in general settings with more complicated nonlinear behaviours higher order terms might need to be included, this however introduce intractable computational complexity.}
\end{itemize}

>>>>

While EKS has been  applied in the context of EM algorithm for learning a nonlinear model from data \cite{Ghahramani1999} this is the first work (to the best authors' knowlege) where the URTSS has been used to perform state inference in the E-step of the EM algorithm. However, as in the case of EKS since an approximate lower bound is maximised at each time step there is no guarantee that URTSS increases the lower bound on the true likelihood function and therefore the stability of the algorithm cannot be ensured. Nevertheless, the proposed framework is more stable due to better performance of the URTSS.

In almost all applications a sequence of likelihood converges to some stationary values i.e. global (local) maximum or a saddle point. If the sequence of EM is trapped in a saddle point a small random purturbation diverges the EM from the saddle point \cite{McLachlan1997}. In general convergence of the EM algorithm to any stationary point either global (local) maxima or saddle points 
depends on the initialisation. Here a bounded sequence of state vectors were used to initialise the algorithm which gives a satisfactory convergence and good state and good parameter estimations.
\begin{itemize}
	\item itterative EM and correlation analysis (maybe)
	\item{comment on EM might convrge to suboptimal solution,simulated
annealing can be used to tackle such situations but difficult to implement (Mc Lachlan)}
	\item{since the non-linearity is a sigmoid function first-order Taylor provide a good approximation however in general settings with more complicated nonlinear behaviours higher order terms might need to be included, this however introduce intractable computational complexity.}
\end{itemize}
